
---
title: "HEALTHYCLOUD FAIRness evaluation tool"
author: Document produced by HealthyCloud
date: "`r format(Sys.time())`"
output:
  html_document:
    df_print: paged
    number_section: yes
    theme: default
    toc: no
    toc_depth: 2
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(
  eval = TRUE,
	echo = TRUE,
	fig.align = "center",
	message = FALSE,
	warning = FALSE,
	fig.width=5.5,
	out.width = "100%"
)
# clean environment
rm(list=ls())
gc()
```



```{r, include=FALSE}

csv_location <- "./FAIRevaluation.csv"

data_collection <- 'Give a title to your data collection FAIR assessment'

q1_a <- ''
q1_b <- ''
q1_c <- 'selected'
q1_d <- ''

q2_0 <- ''
q2_a <- ''
q2_b <- ''
q2_c <- 'selected'

q3_0 <- ''
q3_a <- ''
q3_b <- ''
q3_c <- ''
q3_d <- ''
q3_e <- 'selected'

q4_0 <- ''
q4_a <- ''
q4_b <- ''
q4_c <- 'selected'
q4_d <- ''

q5_a <- ''
q5_b <- ''
q5_c <- 'selected'
q5_d <- ''

q6_a <- ''
q6_b <- ''
q6_c <- ''
q6_d <- ''
q6_e <- ''
q6_f <- 'selected'

q7_a <- ''
q7_b <- ''
q7_c <- ''
q7_d <- 'selected'

q8_a <- ''
q8_b <- ''
q8_c <- ''
q8_d <- ''
q8_e <- 'selected'
q8_f <- ''

q9_a <- ''
q9_b <- ''
q9_c <- ''
q9_d <- ''
q9_e <- 'selected'
q9_f <- ''

q10_a <- ''
q10_b <- ''
q10_c <- 'selected'
q10_d <- ''

q11_a <- ''
q11_b <- ''
q11_c <- 'selected'
q11_d <- ''

q12_a <- ''
q12_b <- ''
q12_c <- 'selected'
q12_d <- ''

q13_a <- ''
q13_b <- ''
q13_c <- 'selected'
q13_d <- ''

q14_a <- ''
q14_b <- ''
q14_c <- ''
q14_d <- 'selected'


```





```{r, include=FALSE}

if (file.exists(csv_location)) {

my_csv2 <- read.csv2(file = csv_location, header=FALSE)

data_collection <- my_csv2[1]

q1_a <- ''
q1_b <- ''
q1_c <- ''
q1_d <- ''

q2_0 <- ''
q2_a <- ''
q2_b <- ''
q2_c <- ''

q3_0 <- ''
q3_a <- ''
q3_b <- ''
q3_c <- ''
q3_d <- ''
q3_e <- ''

q4_0 <- ''
q4_a <- ''
q4_b <- ''
q4_c <- ''
q4_d <- ''

q5_a <- ''
q5_b <- ''
q5_c <- ''
q5_d <- ''

q6_a <- ''
q6_b <- ''
q6_c <- ''
q6_d <- ''
q6_e <- ''
q6_f <- ''

q7_a <- ''
q7_b <- ''
q7_c <- ''
q7_d <- ''

q8_a <- ''
q8_b <- ''
q8_c <- ''
q8_d <- ''
q8_e <- ''
q8_f <- ''

q9_a <- ''
q9_b <- ''
q9_c <- ''
q9_d <- ''
q9_e <- ''
q9_f <- ''

q10_a <- ''
q10_b <- ''
q10_c <- ''
q10_d <- ''

q11_a <- ''
q11_b <- ''
q11_c <- ''
q11_d <- ''

q12_a <- ''
q12_b <- ''
q12_c <- ''
q12_d <- ''

q13_a <- ''
q13_b <- ''
q13_c <- ''
q13_d <- ''

q14_a <- ''
q14_b <- ''
q14_c <- ''
q14_d <- ''


if (my_csv2[21] == 'q1a') {q1_a <- 'selected'}
if (my_csv2[21] == 'q1b') {q1_b <- 'selected'}
if (my_csv2[21] == 'q1c') {q1_c <- 'selected'}
if (my_csv2[21] == 'q1d') {q1_d <- 'selected'}

if (my_csv2[22] == 'q2a') {q2_a <- 'selected'}
if (my_csv2[22] == 'q2b') {q2_b <- 'selected'}
if (my_csv2[22] == 'q2c') {q2_c <- 'selected'}

if (my_csv2[23] == 'q3a') {q3_a <- 'selected'}
if (my_csv2[23] == 'q3b') {q3_b <- 'selected'}
if (my_csv2[23] == 'q3c') {q3_c <- 'selected'}
if (my_csv2[23] == 'q3d') {q3_d <- 'selected'}
if (my_csv2[23] == 'q3e') {q3_e <- 'selected'}

if (my_csv2[24] == 'q4a') {q4_a <- 'selected'}
if (my_csv2[24] == 'q4b') {q4_b <- 'selected'}
if (my_csv2[24] == 'q4c') {q4_c <- 'selected'}
if (my_csv2[24] == 'q4d') {q4_d <- 'selected'}

if (my_csv2[25] == 'q5a') {q5_a <- 'selected'}
if (my_csv2[25] == 'q5b') {q5_b <- 'selected'}
if (my_csv2[25] == 'q5c') {q5_c <- 'selected'}
if (my_csv2[25] == 'q5d') {q5_d <- 'selected'}

if (my_csv2[26] == 'q6a') {q6_a <- 'selected'}
if (my_csv2[26] == 'q6b') {q6_b <- 'selected'}
if (my_csv2[26] == 'q6c') {q6_c <- 'selected'}
if (my_csv2[26] == 'q6d') {q6_d <- 'selected'}
if (my_csv2[26] == 'q6e') {q6_e <- 'selected'}
if (my_csv2[26] == 'q6f') {q6_f <- 'selected'}

if (my_csv2[27] == 'q7a') {q7_a <- 'selected'}
if (my_csv2[27] == 'q7b') {q7_b <- 'selected'}
if (my_csv2[27] == 'q7c') {q7_c <- 'selected'}
if (my_csv2[27] == 'q7d') {q7_d <- 'selected'}

if (my_csv2[28] == 'q14a') {q14_a <- 'selected'}
if (my_csv2[28] == 'q14b') {q14_b <- 'selected'}
if (my_csv2[28] == 'q14c') {q14_c <- 'selected'}
if (my_csv2[28] == 'q14d') {q14_d <- 'selected'}

if (my_csv2[29] == 'q8a') {q8_a <- 'selected'}
if (my_csv2[29] == 'q8b') {q8_b <- 'selected'}
if (my_csv2[29] == 'q8c') {q8_c <- 'selected'}
if (my_csv2[29] == 'q8d') {q8_d <- 'selected'}
if (my_csv2[29] == 'q8e') {q8_e <- 'selected'}
if (my_csv2[29] == 'q8f') {q8_f <- 'selected'}

if (my_csv2[30] == 'q9a') {q9_a <- 'selected'}
if (my_csv2[30] == 'q9b') {q9_b <- 'selected'}
if (my_csv2[30] == 'q9c') {q9_c <- 'selected'}
if (my_csv2[30] == 'q9d') {q9_d <- 'selected'}
if (my_csv2[30] == 'q9e') {q9_e <- 'selected'}
if (my_csv2[30] == 'q9f') {q9_f <- 'selected'}

if (my_csv2[31] == 'q10a') {q10_a <- 'selected'}
if (my_csv2[31] == 'q10b') {q10_b <- 'selected'}
if (my_csv2[31] == 'q10c') {q10_c <- 'selected'}
if (my_csv2[31] == 'q10d') {q10_d <- 'selected'}

if (my_csv2[32] == 'q11a') {q11_a <- 'selected'}
if (my_csv2[32] == 'q11b') {q11_b <- 'selected'}
if (my_csv2[32] == 'q11c') {q11_c <- 'selected'}
if (my_csv2[32] == 'q11d') {q11_d <- 'selected'}

if (my_csv2[33] == 'q12a') {q12_a <- 'selected'}
if (my_csv2[33] == 'q12b') {q12_b <- 'selected'}
if (my_csv2[33] == 'q12c') {q12_c <- 'selected'}
if (my_csv2[33] == 'q12d') {q12_d <- 'selected'}

if (my_csv2[34] == 'q13a') {q13_a <- 'selected'}
if (my_csv2[34] == 'q13b') {q13_b <- 'selected'}
if (my_csv2[34] == 'q13c') {q13_c <- 'selected'}
if (my_csv2[34] == 'q13d') {q13_d <- 'selected'}

}

```



# Data collection


<!-- jQuery (necessary for Bootstrap's JavaScript plugins)
<script src=https://ajax.googleapis.com/ajax/libs/jquery/1.11.1/jquery.min.js></script>
 -->

<!-- Bootstrap via CDN -->
<link rel=stylesheet href=https://maxcdn.bootstrapcdn.com/bootstrap/3.2.0/css/bootstrap.min.css>

<!-- Optional theme -->
<link rel=stylesheet href=https://maxcdn.bootstrapcdn.com/bootstrap/3.2.0/css/bootstrap-theme.min.css/>

<!-- Latest compiled and minified JavaScript -->
<script src=https://maxcdn.bootstrapcdn.com/bootstrap/3.2.0/js/bootstrap.min.js></script>


<style>
canvas {
-moz-user-select: none;
-webkit-user-select: none;
-ms-user-select: none;
}

.w3-container:after,.w3-container:before,.w3-panel:after,.w3-panel:before,.w3-row:after,.w3-row:before,.w3-row-padding:after,.w3-row-padding:before,
.w3-cell-row:before,.w3-cell-row:after,.w3-clear:after,.w3-clear:before,.w3-bar:before,.w3-bar:after{content:'';display:table;clear:both}
.w3-padding{padding:8px 0px!important}
.w3-green,.w3-hover-green:hover{color:#fff!important;background-color:#4CAF50!important}
.w3-border{border:1px solid #ccc!important}

.glyphicon-info-sign {font-size: 1.3em; color: #328cc7;}

a:link {color: #007B9A;}

a:visited {color: #007B9A;}
a {color: #007B9A;}

blockquote {
  font-size: 1.0em;
  margin-left: 6px;}

</style>

<script>

$('document').ready(initialise);
function initialise() {
$(document).on('change', 'select', function() {
update();
// if you want to do stuff based on the OPTION element:
//var opt = $(this).find('option:selected')[0];
});
update();
}


function update() {


var fscore = parseInt($('#q1').val()) + parseInt($("#q2").val()) + parseInt($('#q3').val()) + parseInt($('#q4').val());
$("#fbar").attr('style', "width: " +  (fscore / 17.0) * 100 + "%");
$("#fscore").html(parseInt((fscore / 17.0) * 100) + "%");
$("#fstars").html(createStars(fscore/17.0 * 5));

var ascore = parseInt($("#q5").val()) + parseInt($("#q6").val()) + parseInt($("#q7").val()) + parseInt($("#q14").val());
$("#abar").attr('style', "width: " +  (ascore / 10.0) * 100 + "%");
$("#ascore").html(parseInt((ascore / 10.0) * 100) + "%");
$("#astars").html(createStars(ascore/10.0 * 5));

var iscore = parseInt($("#q8").val()) + parseInt($("#q9").val()) + parseInt($("#q10").val());
$("#ibar").attr('style', "width: " +  (iscore / 8.0) * 100 + "%");
$("#iscore").html(parseInt((iscore / 8.0) * 100) + "%");
$("#istars").html(createStars(iscore/8.0 * 5));

var rscore = parseInt($("#q11").val()) + parseInt($("#q12").val()) + parseInt($("#q13").val());
$("#rbar").attr('style', "width: " +  (rscore / 7.0) * 100 + "%");
$("#rscore").html(parseInt((rscore / 7.0) * 100) + "%");
$("#rstars").html(createStars(rscore/7.0 * 5));

var tscore = fscore / 17 + ascore / 10.0 + iscore / 8.0 + rscore / 7.0;
$("#tbar").attr('style', "width: " +  tscore * 25.0 + "%");
$("#tscore").html(tscore);


$("#tpercentage").html(parseInt(tscore * 25.0) + "%");
console.log(tscore)
$("#tstars").html(createStars(tscore/4.0 * 5));

$("#q1_answer").html('<i>' + $("#q1 option:selected").text() + '</i>');
$("#q1_score").html($("#q1").val());

$("#q2_answer").html('<i>' + $("#q2 option:selected").text() + '</i>');
$("#q2_score").html($("#q2").val());

$("#q3_answer").html('<i>' + $("#q3 option:selected").text() + '</i>');
$("#q3_score").html($("#q3").val());

$("#q4_answer").html('<i>' + $("#q4 option:selected").text() + '</i>');
$("#q4_score").html($("#q4").val());

$("#f_total").html(fscore);

$("#q5_answer").html('<i>' + $("#q5 option:selected").text() + '</i>');
$("#q5_score").html($("#q5").val());

$("#q6_answer").html('<i>' + $("#q6 option:selected").text() + '</i>');
$("#q6_score").html($("#q6").val());

$("#q7_answer").html('<i>' + $("#q7 option:selected").text() + '</i>');
$("#7_score").html($("#q7").val());

$("#q14_answer").html('<i>' + $("#q14 option:selected").text() + '</i>');
$("#14_score").html($("#q14").val());

$("#a_total").html(ascore);

$("#q8_answer").html('<i>' + $("#q8 option:selected").text() + '</i>');
$("#q8_score").html($("#q8").val());
$("#q9_answer").html('<i>' + $("#q9 option:selected").text() + '</i>');
$("#q9_score").html($("#q9").val());
$("#q10_answer").html('<i>' + $("#q10 option:selected").text() + '</i>');
$("#q10_score").html($("#q10").val());
$("#i_total").html(iscore);

$("#q11_answer").html('<i>' + $("#q11 option:selected").text() + '</i>');
$("#q11_score").html($("#q11").val());
$("#q12_answer").html('<i>' + $("#q12 option:selected").text() + '</i>');
$("#q12_score").html($("#q12").val());
$("#q13_answer").html('<i>' + $("#q13 option:selected").text() + '</i>');
$("#q13_score").html($("#q13").val());
$("#r_total").html(rscore);


}

function createStars(score) {
var blank = '<span class="glyphicon glyphicon-star-empty" aria-hidden="true"></span>';
var filled = '<span class="glyphicon glyphicon-star" aria-hidden="true"></span>';
var html = "";
var i = 0;
score = Math.floor(score);

while (i < 5) {
if (score > i) {
html += filled;
} else {
html += blank;
}
i += 1;
}
return html;
}

</script>



<div class="container">




<div class="bs-example">
<div class="panel-group" id="accordion">
<form>
<input class="form-control" id="q0"  type="text"  name="q0" value="`r toString(data_collection)`" style="font-size: 1.8em;">
</form>

<BR>


<p>This FAIRness evaluation tool has been created by members of the <A HREF="https://healthycloud.eu/" TARGET="_blank">HealthyCloud consortium</A>, specifically Work Package 3 (WP3). The tool is based on the Australian Research Data Commons (ARDC) <A HREF="https://ardc.edu.au/resources/aboutdata/fair-data/fair-self-assessment-tool/" TARGET=_blank>FAIR data self-assessment tool</A>.</p>

<p>This 2-in-1 tool (survey form and reporting) is designed to allow assessment of the FAIRness of health-related data infrastructures, and includes questions to assess each of the FAIR principles. These questions are based on a survey developed by members of the consortium with the aim of carrying out a landscape analysis of health-related data infrastructures.</p>

<p>There is an option to select 'I don't know' under each question. However, we would encourage users to consider if there is someone else in their organisation who does know the answer to that question, to increase the accuracy of the assessment. You would need to share the FAIRness report within your organisation. At each updating step, a new csv file can be produced and used to generate an updated FAIRness report.</p>

<p>Step by step guide for users:</p>
<UL>
<LI>Input your answers for each question in the tool
<LI>Click 'Download' and save the csv file
<LI>Re-run the script*, specifying the location at which the csv file has been saved
<LI>This creates a FAIRness report, including pie charts demonstrating the percentage scores for each principle as well as an overall score.
<LI>Save and share the FAIRness report as an HTML document.
</UL>

<p>[*] The tool can be downloaded on <A HREF="https://zenodo.org/" TARGET="_blank">ZENODO.org</A> (<A HREF="https://www.rstudio.com/" TARGET="_blank">R studio</A> is required) or accessed on <A HREF="https://ovh.mybinder.org/v2/gh/PderyckeSciensano/HEALHTYCLOUD/main?urlpath=rstudio" TARGET="_blank">MyBinder</A>.</p>


# FAIR survey


<!-- Findable -->
<div class="panel panel-default">
<div class="panel-heading">
<h4 class="panel-title">
<a data-toggle="collapse" href="#collapseOne">Findable</a>
</h4>
</div>
<!--<div id="collapseOne" class="panel-collapse collapse in"> -->
<div id="collapseOne" class="panel-collapse collapse">
<div class="panel-body">
<form>

<!-- QUESTION Findable 1 -->
<div class="form-group row">
<label for="q1" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q1"></a>

<blockquote>Do you have a unique identifier for your datasets?</blockquote>



</label>

<div class="col-sm-6">

<select class="form-control" id="q1" name="q1">
<option id="q1a" value="5" `r toString(q1_a)`>Yes (5)</option>
<option id="q1b" value="0" `r toString(q1_b)`>No (0)</option>
<option id="q1d" value="0" `r toString(q1_d)`>This question doesn't apply to this data infrastructure (0)</option>
<option id="q1c" value="0" `r toString(q1_c)`>I don't know (0)</option>

</select>

</div>
</div>


<!-- QUESTION Findable 2 -->
<div class="form-group row">
<label for="q2" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q2"></a>

<blockquote>Do you have a unique identifier for the metadata?</blockquote>


</label>

<div class="col-sm-6">

<select class="form-control" id="q2" name="q2">
<option id="q2a" value="4" `r toString(q2_a)`>Yes (4)</option>
<option id="q2b" value="0" `r toString(q2_b)`>No (0)</option>
<option id="q2c" value="0" `r toString(q2_c)`>I don't know (0)</option>
</select>

</div>
</div>

<!-- QUESTION Findable 3 -->
<div class="form-group row">
<label for="q3" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q3"></a>

<blockquote>Do you produce or collect metadata for all your data (e.g. handbook, guide for users, description, keywords, timestamp, spatial coverage etc.)?</blockquote>


</label>

<div class="col-sm-6">

<select class="form-control" id="q3" name="q3">
<option id="q3a" value="4" `r toString(q3_a)`>Comprehensively (see suggestion) using a recognised formal machine-readable metadata schema. (4)</option>
<option id="q3b" value="3" `r toString(q3_b)`>Comprehensively, but in a text-based, non-standard format. (3)</option>
<option id="q3c" value="2" `r toString(q3_c)`>Brief title and description (2)</option>
<option id="q3d" value="0" `r toString(q3_d)`>The data is not described (0)</option>
<option id="q3e" value="0" `r toString(q3_e)`>I don't know (0)</option>

</select>
</div>
</div>


<!-- QUESTION Findable 4 -->
<div class="form-group row">
<label for="q4" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q4"></a>

<blockquote>Do you have a public metadata catalogue service?</blockquote>


</label>

<div class="col-sm-6">

<select class="form-control" id="q4" name="q4">
<option id="q4a" value="4" `r toString(q4_a)`>Yes (4)</option>
<option id="q4b" value="0" `r toString(q4_b)`>No (0)</option>
<option id="q4d" value="0" `r toString(q4_d)`>This question doesn't apply to this data infrastructure (0)</option>
<option id="q4c" value="0" `r toString(q4_c)`>I don't know (0)</option>

</select>

</div>
</div>
</form>
<div class="w3-border">
<div id="fbar" class="w3-container w3-padding w3-green" style="width:0;">
<div class="w3-center" id="demo"></div>
</div>
</div>
</div>
</div>
</div>






<!-- Accessible -->
<div class="panel panel-default">
<div class="panel-heading">
<h4 class="panel-title">
<a data-toggle="collapse" href="#collapseTwo">Accessible</a>
</h4>
</div>
<div id="collapseTwo" class="panel-collapse collapse">
<div class="panel-body">
<form>

<!-- QUESTION Accessible 1 -->
<div class="form-group row">
<label for="q5" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q5"></a>

<blockquote>Do you provide access to individual and/or aggregated data (for third party users)?</blockquote>

</label>

<div class="col-sm-6">

<select class="form-control" id="q5" name="q5">
<option id="q5a" value="4"`r toString(q5_a)`>Publicly accessible individual and aggregated (4)</option>
<option id="q5b" value="3" `r toString(q5_b)`>Publicly accessible aggregated (3)</option>
<option id="q5d" value="0" `r toString(q5_d)`>This doesn't apply to this data infrastructure (0)</option>
<option id="q5c" value="0" `r toString(q5_c)`>I don't know (0)</option>

</select>

</div>
</div>

<!-- QUESTION Accessible 2 -->
<div class="form-group row">
<label for="q6" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q6"></a>

<blockquote>Is it possible to extract the data from the data infrastructure (e.g. download) or do they have to stay in the data infrastructure?</blockquote>

</label>

<div class="col-sm-6">

<select class="form-control" id="q6" name="q6">
<option id="q6a" value="4" `r toString(q6_a)`>Standard web service API (e.g. OGC) (4)</option>
<option id="q6b" value="3" `r toString(q6_b)`>Non-standard web service (e.g. OpenAPI/Swagger/informal API) (3)</option>
<option id="q6c" value="2" `r toString(q6_c)`>File download from online location (2)</option>
<option id="q6d" value="1" `r toString(q6_d)`>By individual arrangement (1)</option>
<option id="q6e" value="0" `r toString(q6_e)`>No access to data (0)</option>
<option id="q6f" value="0" `r toString(q6_f)`>I don't know (0)</option>

</select>
</div>
</div>

<!-- QUESTION Accessible 3 -->
<div class="form-group row">
<label for="q7" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q7"></a>

<blockquote>Do third party users have to register to the data infrastructure and have an account in order to access the data?</blockquote>

</label>

<div class="col-sm-6">

<select class="form-control" id="q7" name="q7">
<option id="q7a" value="1" `r toString(q7_a)`>Yes (1)</option>
<option id="q7b" value="0" `r toString(q7_b)`>No (0)</option>
<option id="q7c" value="0" `r toString(q7_c)`>Unsure (0)</option>
<option id="q7d" value="0" `r toString(q7_d)`>I don't know (0)</option>
</select>

</div>
</div>


<!-- QUESTION Accessible 4 -->
<div class="form-group row">
<label for="q14" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q14"></a>

<blockquote>Are the conditions of access published?</blockquote>

</label>

<div class="col-sm-6">
<select class="form-control" id="q14" name="q14">

<option id="q14a" value="1" `r toString(q14_a)`>Yes (1)</option>
<option id="q14b" value="0" `r toString(q14_b)`>No (0)</option>
<option id="q14c" value="0" `r toString(q14_c)`>Unsure (0)</option>
<option id="q14d" value="0" `r toString(q14_d)`>I don't know (0)</option>

</select>
</div>
</div>



</form>
<div class="w3-border">
<div id="abar" class="w3-container w3-padding w3-green" style="width:1%">
<div class="w3-center" id="idemo"></div>
</div>
</div>

</div>
</div>
</div>

<!-- Interoperable -->
<div class="panel panel-default">
<div class="panel-heading">
<h4 class="panel-title">
<a data-toggle="collapse" href="#collapseThree">Interoperable</a>
</h4>
</div>
<div id="collapseThree" class="panel-collapse collapse">
<div class="panel-body">
<form>

<!-- QUESTION Interoperable 1 -->
<div class="form-group row">
<label for="q8" class="col-sm-6 col-form-label">
<a href="#reusable_info" data-toggle="modal" data-target="#info_q8"></a>

<blockquote>What is the format(s) for distributing data?</blockquote>

</label>

<div class="col-sm-6">
<select class="form-control" id="q8" name="q8">

<option id="q8a" value="4" `r toString(q8_a)`>In a structured, open standard, machine-readable format (csv, xml, json, R, ...)(4) </option>
<option id="q8b" value="2" `r toString(q8_b)`>In a structured, open standard, non-machine-readable format (2) (pdf)</option>
<option id="q8c" value="0" `r toString(q8_c)`>Mostly in a proprietary format (SAS) (0)</option>
<option id="q8d" value="0" `r toString(q8_d)`>Other (0)</option>
<option id="q8f" value="0" `r toString(q8_f)`>This doesn't apply to this data infrastructure</option>
<option id="q8e" value="0" `r toString(q8_e)`>I don't know (0)</option>

</select>
</div>
</div>

<!-- QUESTION Interoperable 2 -->
<div class="form-group row">
<label for="q9" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q9"></a>

<blockquote>Which community-recognised vocabularies, standards or methodologies are used for metadata and data to facilitate interoperability?</blockquote>

</label>

<div class="col-sm-6">
<select class="form-control" id="q9" name="q9">

<option id="q9a" value="2" `r toString(q9_a)`>Standardised open and universal using resolvable global identifiers linking to explanations  (OPen ex: ...) (2)</option>
<option id="q9b" value="1" `r toString(q9_b)`>Standardised vocabularies/ontologies/schema without global identifiers (HL7, FHIR, SNOMED CT, LOINC, ICD-10,...) (1)</option>
<option id="q9c" value="1" `r toString(q9_c)`>Other (1)</option>
<option id="q9d" value="0" `r toString(q9_d)`>Data elements not described (0)</option>
<option id="q9e" value="0" `r toString(q9_e)`>I don't know (0)</option>
<option id="q9f" value="0" `r toString(q9_f)`>This doesn't apply to this data infrastructure (0)</option>

</select>
</div>
</div>

<!-- QUESTION Interoperable 3 -->
<div class="form-group row">
<label for="q10" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q10"></a>

<blockquote>Do you have a metadata record API endpoint (m2m) in place?</blockquote>

</label>

<div class="col-sm-6">
<select class="form-control" id="q10" name="q10">

<option id="q10a" value="2" `r toString(q10_a)`>Yes (2)</option>
<option id="q10b" value="0" `r toString(q10_b)`>No (0)</option>
<option id="q10d" value="0" `r toString(q10_d)`>This question doesn't apply to this data infrastructure (0)</option>
<option id="q10c" value="0" `r toString(q10_c)`>I don't know</option>

</select>
</div>
</div>


</form>
<div class="w3-border">
<div id="ibar" class="w3-container w3-padding w3-green" style="width:1%">
<div class="w3-center" id="iidemo"></div>
</div>
</div>


</div>
</div>
</div>

<!-- Reusable -->
<div class="panel panel-default">
<div class="panel-heading">
<h4 class="panel-title">
<a data-toggle="collapse" href="#collapseFour">Reusable</a>
</h4>
</div>
<div id="collapseFour" class="panel-collapse collapse">
<div class="panel-body">
<form>

<!-- QUESTION Reusable 1 -->
<div class="form-group row">
<label for="q11" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q11"></a>

<blockquote>Is there a clear procedure for third party users to request (the license) for data re-use?</blockquote>

</label>

<div class="col-sm-6">
<select class="form-control" id="q11" name="q11">

<option id="q11a" value="3" `r toString(q11_a)`>Yes (3)</option>
<option id="q11b" value="0" `r toString(q11_b)`>No(0)</option>
<option id="q11e" value="0" `r toString(q11_d)`>This question doesn't apply to this data infrastructure (0)</option>
<option id="q11c" value="0" `r toString(q11_c)`>I don't know (0)</option>

</select>
</div>
</div>

<!-- QUESTION Reusable 2 -->
<div class="form-group row">
<label for="q12" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q12"></a>

<blockquote>Have you placed the metadata related to your data infrastructure (that is, the above information provided in this survey) in another available source already?</blockquote>

</label>

<div class="col-sm-6">
<select class="form-control" id="q12" name="q12">

<option id="q12a" value="2" `r toString(q12_a)`>Yes (2)</option>
<option id="q12b" value="0" `r toString(q12_b)`>No (0)</option>
<option id="q12d" value="0" `r toString(q12_d)`>This question doesn't apply to this data infrastructure (0)</option>
<option id="q12c" value="0" `r toString(q12_c)`>I don't know (0)</option>

</select>
</div>
</div>


<!-- QUESTION Reusable 3 -->
<div class="form-group row">
<label for="q13" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q13"></a>

<blockquote>Is it possible for third party users to access the data and re-use it for more than one purpose/project?</blockquote>

</label>

<div class="col-sm-6">
<select class="form-control" id="q13" name="q13">

<option id="q13a" value="2" `r toString(q13_a)`>Yes (2)</option>
<option id="q13b" value="0" `r toString(q13_b)`>No (0)</option>
<option id="q13d" value="0" `r toString(q13_d)`>This question doesn't apply to this data infrastructure (0)</option>
<option id="q13c" value="0" `r toString(q13_c)`>I don't know (0)</option>

</select>
</div>
</div>



</form>
<div class="w3-border">
<div id="rbar" class="w3-container w3-padding w3-green" style="width:1%">
<div class="w3-center" id="rdemo"></div>
</div>
</div>


</div>
</div>
</div>
</div>

<h4>FAIRNESS score <span id="tpercentage"></span></h4>

<div class="w3-border">
<div id="tbar" class="w3-container w3-padding w3-green" style="width:0%">
<div class="w3-center" id="tdemo"></div>
</div>
</div>
<p>

<form id="form">

<!--<p> Stars <span id="tstars"></span></p>-->
<!--<p> FAIRNESS total score <span id="tscore"></span></p>-->


<table width=100%>
<TR><TD>FINDABLE</TD><TD>ACCESSIBLE</TD><TD>INTEROPERABLE</TD><TD>REUSABLE</TD></TR>
<TR><TD><span id="fscore"></span></TD><TD><span id="ascore"></TD><TD><span id="iscore"></TD><TD><span id="rscore"></span></TD></TR>
<TR><TD COLSPAN=4><hr/></TD></TR>



<input class="form-control" type="hidden" id="findablescore" name="findablescore" value="" />
<input class="form-control" type="hidden" id="accessiblescore" name="accessiblescore" value="" />
<input class="form-control" type="hidden" id="interopscore" name="interopscore" value="" />
<input class="form-control" type="hidden" id="reusescore" name="reusescore" value="" />
<input class="form-control" type="hidden" id="totalscore" name="totalscore" value="" />

<input class="form-control" type="hidden" id="findable1" name="findable1" value="" />
<input class="form-control" type="hidden" id="findable2" name="findable2" value="" />
<input class="form-control" type="hidden" id="findable3" name="findable3" value="" />
<input class="form-control" type="hidden" id="findable4" name="findable4" value="" />

<input class="form-control" type="hidden" id="accessible1" name="accessible1" value="" />
<input class="form-control" type="hidden" id="accessible2" name="accessible2" value="" />
<input class="form-control" type="hidden" id="accessible3" name="accessible3" value="" />
<input class="form-control" type="hidden" id="accessible4" name="accessible4" value="" />

<input class="form-control" type="hidden" id="interoperable1" name="interoperable1" value="" />
<input class="form-control" type="hidden" id="interoperable2" name="interoperable2" value="" />
<input class="form-control" type="hidden" id="interoperable3" name="interoperable3" value="" />

<input class="form-control" type="hidden" id="reusable1" name="reusable1" value="" />
<input class="form-control" type="hidden" id="reusable2" name="reusable2" value="" />
<input class="form-control" type="hidden" id="reusable3" name="reusable3" value="" />

<TR><TD COLSPAN=4 ALIGN=center><input type="button" value="Download csv file" id="dl" onclick="submitForm();"></TD></TR>

<table>

</form>



# FAIR report



```{r, echo=FALSE, out.width='60%'}


if (file.exists(csv_location)) {

library(dplyr)
library(ggplot2)


findable=c(as.integer(my_csv2[2])/17*100+ as.integer(my_csv2[3])/17*100+as.integer(my_csv2[4])/17*100+as.integer(my_csv2[5])/17*100,(17-as.integer(my_csv2[2])-as.integer(my_csv2[3])-as.integer(my_csv2[4])-as.integer(my_csv2[5]))/17*100)


df <- data.frame(
Findable = c("Findable", "Not findable"), value = findable)


bp<- ggplot(df, aes(x="", y=value, fill=Findable))+
geom_bar(width = 1, stat = "identity")+
  coord_fixed() +
xlab("") + 
ylab("")

pie <- bp + coord_polar("y", start=0,direction=-1) + ggtitle(paste("Findable",my_csv2[16], sep=" ")) + scale_fill_manual(values = c("Findable"="#f8766d","Not findable"="gray"))
plot(pie)


} else {
  
print('Follow the step by step guide to produce the FAIR report')
  
}

```


```{r, echo=FALSE, out.width='60%'}


if (file.exists(csv_location)) {


accessible=c(as.integer(my_csv2[6])/10*100+ as.integer(my_csv2[7])/10*100+as.integer(my_csv2[8])/10*100+as.integer(my_csv2[9])/10*100,(10-as.integer(my_csv2[6])-as.integer(my_csv2[7])-as.integer(my_csv2[8])-as.integer(my_csv2[9]))/10*100)


df <- data.frame(Accessible = c("Accessible", "Not accessible"), value = accessible)


bp<- ggplot(df, aes(x="", y=value, fill=Accessible))+
geom_bar(width = 1, stat = "identity")+
  coord_fixed() +
xlab("") + 
ylab("")

pie <- bp + coord_polar("y", start=0,direction=-1) + ggtitle(paste("Accessible",my_csv2[17], sep=" ")) + scale_fill_manual(values = c("Accessible"="#00bf7d","Not accessible"="gray"))
plot(pie)


}

```



```{r, echo=FALSE, out.width='60%'}


if (file.exists(csv_location)) {


interoperable=c(as.integer(my_csv2[10])/8*100+ as.integer(my_csv2[11])/8*100+as.integer(my_csv2[12])/8*100,(8-as.integer(my_csv2[10])-as.integer(my_csv2[11])-as.integer(my_csv2[12]))/8*100)


df <- data.frame(Interoperable = c("Interoperable", "Not interoperable"), value = interoperable)


bp<- ggplot(df, aes(x="", y=value, fill=Interoperable))+
geom_bar(width = 1, stat = "identity")+
  coord_fixed() +
xlab("") + 
ylab("")

pie <- bp + coord_polar("y", start=0,direction=-1) + ggtitle(paste("Interoperable",my_csv2[18], sep=" ")) + scale_fill_manual(values = c("Interoperable"="#00b0f6","Not interoperable"="gray"))
plot(pie)


}

```

```{r, echo=FALSE, out.width='60%'}


if (file.exists(csv_location)) {



reuseable=c(as.integer(my_csv2[13])/7*100+ as.integer(my_csv2[14])/7*100+as.integer(my_csv2[15])/7*100,(7-as.integer(my_csv2[13])-as.integer(my_csv2[14])-as.integer(my_csv2[15]))/7*100)


df <- data.frame(Reuseable = c("Reuseable", "Not reuseable"), value = reuseable)

  
bp<- ggplot(df, aes(x="", y=value, fill=Reuseable))+
geom_bar(width = 1, stat = "identity")+
coord_fixed() +
xlab("") + 
ylab("")

pie <- bp + coord_polar("y", start=0,direction=-1) + ggtitle(paste("Reuseable",my_csv2[19], sep=" "))+ scale_fill_manual(values = c("Reuseable"="#e76bf3","Not reuseable"="gray"))
plot(pie)


}


```





```{r, echo=FALSE, out.width='80%'}


if (file.exists(csv_location)) {


Fin_perc<-as.integer(gsub('%', '', my_csv2[16]))*0.25

Acc_perc<-as.integer(gsub('%', '', my_csv2[17]))*0.25

Inter_perc<-as.integer(gsub('%', '', my_csv2[18]))*0.25

Reus_perc<-as.integer(gsub('%', '', my_csv2[19]))*0.25

Tot_perc<-as.integer(gsub('%', '', my_csv2[20]))

  
fair=c(Fin_perc,Acc_perc,Inter_perc,Reus_perc,(100-Tot_perc))


df <- data.frame(FAIR = c("Findable","Accessible","Interoperable","Reusable","Not FAIR"), value = fair)

name0<-paste(Tot_perc," %",sep="")
name1<-paste(my_csv2[19]," (",Reus_perc,"%)",sep="")
name2<-paste(my_csv2[18]," (",Inter_perc,"%)",sep="")
name3<-paste(my_csv2[17]," (",Acc_perc,"%)",sep="")
name4<-paste(my_csv2[16]," (",Fin_perc,"%)",sep="")

bp<- ggplot(df, aes(x="", y=value, fill=FAIR))+
geom_bar(width = 1, stat = "identity")+
xlab("") + 
ylab("")

pie <- bp + coord_polar("y", start=0) + ggtitle(paste("FAIR score ",Tot_perc,"%",sep="")) + scale_fill_manual(values =c("Findable"="#f8766d","Accessible"="#00bf7d","Interoperable"="#00b0f6","Reusable"="#e76bf3","Not FAIR"="gray"))
plot(pie)

fair_eval=c(name4,name3,name2,name1,name0)
FAIR_EVALUATION <- data.frame(FAIRness_Evaluation = c("Findable","Accessible","Interoperable","Reusable","FAIRness score"), value = fair_eval)

FAIR_EVALUATION

}

```













<script>




//Clear form once submitted
function clearForm(){
document.getElementById("form").reset();
}



function submitForm() {

document.getElementById('findablescore').value= document.getElementById("fscore").textContent;
document.getElementById('accessiblescore').value= document.getElementById("ascore").textContent;
document.getElementById('interopscore').value= document.getElementById("iscore").textContent;
document.getElementById('reusescore').value= document.getElementById("rscore").textContent;
document.getElementById('totalscore').value= document.getElementById("tpercentage").textContent;

document.getElementById('findable1').value= q1[q1.selectedIndex].id;
document.getElementById('findable2').value= q2[q2.selectedIndex].id;
document.getElementById('findable3').value= q3[q3.selectedIndex].id;
document.getElementById('findable4').value= q4[q4.selectedIndex].id;

document.getElementById('accessible1').value= q5[q5.selectedIndex].id;
document.getElementById('accessible2').value= q6[q6.selectedIndex].id;
document.getElementById('accessible3').value= q7[q7.selectedIndex].id;
document.getElementById('accessible4').value= q14[q14.selectedIndex].id;

document.getElementById('interoperable1').value= q8[q8.selectedIndex].id;
document.getElementById('interoperable2').value= q9[q9.selectedIndex].id;
document.getElementById('interoperable3').value= q10[q10.selectedIndex].id;

document.getElementById('reusable1').value= q11[q11.selectedIndex].id;
document.getElementById('reusable2').value= q12[q12.selectedIndex].id;
document.getElementById('reusable3').value= q13[q13.selectedIndex].id;




var formData = $("form").serializeArray();
let csv = "data:text/csv;charset=utf-8,"; // accept data as CSV

formData.forEach(function(item) {
csv += item.value + ";"; // concat form value on csv var and add ; to create columns (you can change to , if want)
});

var encodedUri = encodeURI(csv);

// if you want to download
var downloadLink = document.createElement("a");
downloadLink.setAttribute("download", "FAIRevaluation.csv");
downloadLink.setAttribute("href", encodedUri);
document.body.appendChild(downloadLink); // Required for FF
downloadLink.click();
downloadLink.remove();

clearForm();
}
</script>




 
</p>
</div>

</div>













<!-- Trigger the modal with a button
<button type="button" class="btn btn-info btn-lg" data-toggle="modal" data-target="#myModal">Open Modal</button>
-->

<!-- Modal -->
<div id="findable_info" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Findable</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="accessible_info" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Accessible</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="interoperable_info" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Interoperability</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="reusable_info" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Reusable</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_q1" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About identifiers</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="info_q2" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About identifiers</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_q3" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About metadata descriptions</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="info_q4" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About metadata repositories</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>



<div id="info_q5" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About data accessibility</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_q6" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About protocols</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_q7" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About metadata availability</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>





<div id="info_q8" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About file formats</h4>
</div>
<div class="modal-body">
 <p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="info_q9" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About schema standards</h4>
</div>
<div class="modal-body">
 <p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_q10" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About metadata links</h4>
</div>
<div class="modal-body">
 <p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_q11" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About licenses</h4>
</div>
<div class="modal-body">
 <p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="info_q12" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About provenance</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_q13" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">C76</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_fscore" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Findable Score</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="info_ascore" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Accessible Score</h4>
</div>
<div class="modal-body">
<p>.</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_iscore" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modßal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Interoperable Score</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="info_rscore" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Reusable Score</h4>
</div>
<div class="modal-body">
 <p>.</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<BR><BR>

# Open-notebook
Access <A HREF=https://mybinder.org/v2/gh/Marine-Analyst/Jupyter/main?urlpath=rstudio TARGET=_blank>MyBinder.org/HealthyCloud</A> virtual environment.<br>
More info at <A HREF=http://marine-analyst.eu/dev.py?N=50&O=487 TARGET=_blank>Zenodo.eu</A><br>
<p xmlns:cc="http://creativecommons.org/ns#" >This document produced by <span property="cc:attributionName">HealthyCloud FAIR notebook</span> is licensed under <a href="http://creativecommons.org/licenses/by-nc/4.0/?ref=chooser-v1" target="_blank" rel="license noopener noreferrer" style="display:inline-block;">CC BY-NC 4.0<img style="height:22px!important;margin-left:3px;vertical-align:text-bottom;" src="https://mirrors.creativecommons.org/presskit/icons/cc.svg?ref=chooser-v1"><img style="height:22px!important;margin-left:3px;vertical-align:text-bottom;" src="https://mirrors.creativecommons.org/presskit/icons/by.svg?ref=chooser-v1"><img style="height:22px!important;margin-left:3px;vertical-align:text-bottom;" src="https://mirrors.creativecommons.org/presskit/icons/nc.svg?ref=chooser-v1"></a></p>

<BR><BR>

```{r, include=FALSE, results='hide'}
rm(list=ls())
gc()
```

